---
title: "ggplot566"
author: "Eric Peter"
date: "9/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### GGPLOT2 Assignment

This data set contains ratings of every episode from the IMDB top 250 series. Personally, I have heard the "Parks and Rec vs The Office" debate for years now. I would like to see how their IMDB ratings stack up against each other over the course of their series'. 

```{r cars}
ratings <- read.csv("C:/Users/ericp/Downloads/archive/imdb_top_250_series_episode_ratings.csv")
favShows <- c("Parks and Recreation", "The Office")
library(dplyr)
recVsOffice <- ratings %>% 
  filter(Title %in% favShows)
head(recVsOffice)
```
First, the data needed to be filtered to include only these two shows.

```{r}
library(ggplot2)
library(dplyr)
library(directlabels)
plt <- ggplot(data = recVsOffice) + 
  geom_line(aes(x=X, y=Rating, color = Title))  + geom_dl(aes(x=X, y=Rating, color = Title,label=Title), method = 'top.points') + xlab("Episode Number")
plt
```

But what about by season?
```{r}
(recVsOfficeSeasons <- recVsOffice %>% group_by(Season,Title) %>% summarise(Rating = mean(Rating), .groups = "keep"))
plt <- ggplot(data = recVsOfficeSeasons) + 
  geom_line(aes(x=Season, y=Rating, color = Title))  + geom_dl(aes(x=Season, y=Rating, color = Title,label=Title), method = 'top.points') + xlab("Season")
plt
```


Finally, let's look at each series' distribution of ratings.
```{r}
plt <- ggplot(data = recVsOffice) + 
  geom_bar(stat = "count", aes(x=Rating, fill = Title), position = "dodge") + xlab("Rating")
plt
```

